European or American? A re-examination of the transatlantic influence over the IMF

### 2025-07-16 manuscript/manuscript.qmd
update interaction term interpretation

Contrary to the hypothesis of regional favouritism, the interaction terms are either statistically insignificant or, when significant, indicate a *weaker* effect of European influence for European borrowers. For example, in the loan-to-GDP ratio and participation rate models, the negative and significant interaction terms suggest that European influence is associated with *less favourable* outcomes for European recipients compared to non-Europeans.

>>>>

Contrary to the hypothesis of regional favouritism, the results suggest that European recipients do not receive preferential treatment from the IMF or benefit more from their ties to Western European powers. If anything, the estimates indicate that they may even be treated less favourably in some respects. The interaction terms (`EUP Influence $\times$ European recipient`), which capture whether European influence has a differential effect for European borrowers compared to non-European ones, are either statistically insignificant or, when significant, indicate a *weaker* effect for European recipients. For instance, in the loan-to-GDP ratio, participation rate, and IMF conditions models, the negative and significant interaction terms suggest that ties with Western European powers are associated with *less favourable* outcomes for European recipients relative to non-European countries with comparable ties.
